\section{Conclusion}\label{sec:conclusion}
The tool support for JavaScript is especially small compared to its popularity. Developers need to relay on manual testing or unit tests for revealing programming errors. The implemented type checker provides a tool that is capable of inferring the types and catch a variety of errors through type checking. The evaluation shows that the analysis is precise and sound for most of the scenarios and sometime provides better results than competitive tools. Therefore, the tool can provide valuable feedback. 

But the evaluation also indicates that the presented algorithm has its limitations. First, the precision diminishes for reflection-like code. The precision for these cases can be improved if type annotations are used instead of type inference to improve the overall result. Another limitation is the inability to access properties of potential absent values as the analysis is not path-sensitive and therefore, the value is potentially absent in all branches. Path-sensitivity is also required to support type-specific branches, a technique often used to emulate function overloading. 

Further, the set of supported features is not sufficient to analyze real-word projects. The implementation is still missing elementary features, such as classes, prototyping or modules. The tool has to support all these essential features to be useful. Supporting a majority of the features defined in the ECMAScript 6 and the upcoming ECMAScript 7 standard require a tremendous amount of additional work that exceeds the scope of a project thesis by a multitude. But this project thesis shows that precise inference results can be achieved for a majority of JavaScript that --- combined with type checking --- provides a valuable and immediate feedback to programmers. 